Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-12-05 paper/main.tex
add affiliation and acknowledgement for John Soo
partial update on author affil and acknowl

{ \red{personal funding sources}}
SJS acknowledges support from DOE grant DE-SC0009999 and NSF/AURA grant N56981C.
AIM acknowledges support from the Max Planck Society and the Alexander von Humboldt Foundation in the framework of the Max Planck-Humboldt Research Award endowed by the Federal Ministry of Education and Research.
During the completion of this work, AIM was advised by David W. Hogg and was supported by National Science Foundation grant AST-1517237.
%JYHS is advised by Ofer Lahav and acknowledges support from the MyBrainSc Scholarship, provided by the Ministry of Education, Malaysia. JS would also like to thank Antonella Palmese and Boris Leistedt for guidance on the use of the algorithms ANNz2 and Delight respectively.

>>>>

{ \red{personal funding sources}}
SJS acknowledges support from DOE grant DE-SC0009999 and NSF/AURA grant N56981C.
AIM acknowledges support from the Max Planck Society and the Alexander von Humboldt Foundation in the framework of the Max Planck-Humboldt Research Award endowed by the Federal Ministry of Education and Research.
During the completion of this work, AIM was advised by David W. Hogg and was supported by National Science Foundation grant AST-1517237.
JYHS acknowledges financial support from the MyBrainSc Scholarship (Ministry of Education, Malaysia), and the supervision of Ofer Lahav and Benjamin Joachimi.
JYHS would also like to thank Antonella Palmese and Boris Leistedt for guidance on the use of the algorithms ANNz2 and Delight respectively.
MB acknowledges support from the Agreement ASI/INAF 2018-23-HH.0 - Phase D.
AJC and JBK acknowledges support from DOE grant DE-SC-0011635. AJC, JBK, MLG, CBM acknowledge support from the DIRAC Institute in the Department of Astronomy at the University of Washington. The DIRAC Institute is supported through generous gifts from the Charles and Lisa Simonyi Fund for Arts and Sciences, and the Washington Research Foundation.
MJJ acknowledges support from Oxford Hintze Centre for Astrophysical Surveys which is funded through generous support from the Hintze Family Charitable Foundation.
